\documentclass[a4paper,12pt]{report}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[a4paper,total={6in,8in}]{geometry}

\doublespacing \begin{document}


\chapter*{\centering DailyClicQ}
\begin{center}
{\Large  MIDHUN MK }\\

{\large KMC18MCA007}

\end{center}
\chapter*{\centering Abstract}

	\setstretch{2.0}\hspace*{12pt} E-Commerce today is a way of life and an extremely integral part of modern day shopping. DailyClicQ presents in front of you, a unique online shopping experience with its huge variety of products from numerous categories, making it a one stop shop for all daily needs. The DailyClicQ is truly standing by the tagline of the Regional Shopping Portal in India.\\

\hspace*{12pt}DailyClicQ, the place to find the best Products for every taste and occasion. Working only with reliable suppliers so that you only receive the best quality product. I believe shopping is a right, not a luxury, so we strive to deliver the best products at the most affordable prices, and ship them to you regardless of where you are located.\\
\newpage
\hspace*{12pt}The DailyClicQ will consist of 3 users the Admin, Vendors and the Customers. Lets discuss about the Admin, the segments that i am going to perform over the admin module is first to give the right to approve or reject the registeration of any vendor who are requesting to be a part of the DailyClicQ then the next segment contains the feature of editing or deleting the Vendor's details. The product added by the vendor to the site will be decided by the Admin whether to approve or reject that product is the another segment in the Admin Module. And the last segment of the Admin module will be Managing of the orders details and Users details inshort keeping their reports.\\

\hspace*{12pt}The Segments i am going to perform in Vendors will be of giving the right for adding the products based on the category and the category will be such as Mobile \& Accessories, Laptop and Computers, Electronic \& Applications Mens Wardrobe, Womens Wardrobe, Kids Fashion, Home \& Kitchens, Beauty Products, Sports, Automobile Accessories \& Spare parts, Grocery items. And over this products the vendor will be allowed to perform the update and delete operation and that will be the next segment in this module. Adding offers to the products according to the certain occasion will be the next segments. And the last segment in the vendors is to provide a coin feature which will be a kind of offer on the basis of purchasing goods from the site for the customers and the Vendors will have the responsibility of Managing order details inshort keeping their reports.\\

\hspace*{12pt}At last in the Customers module i am going to give the functionality of finding the necessary goods from the site according to the affordable prices and looking towards the nearby shops. And at last after the product selection and placing the order the vendor will ship the product to wherever the customer is located.

  

\end{document}