\documentclass[a4paper,12pt]{report}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[a4paper,total={6in,8in}]{geometry}

\doublespacing \begin{document}


\chapter*{\centering Rental Management}
\begin{center}
{\Large  Rismin M.T. }\\


\end{center}
\chapter*{\centering Abstract}

	\setstretch{2.0}\hspace*{12pt}The growth of internet has greatly enhanced various business processes and communication between company (services provider) and their customers of which Vehicle rental industry is not left out. This Vehicle Rental System is developed to provide the many services, Enhance Business Processes: To be able to use internet technology to project the rental company to the global world instead of limiting their services to their local domain alone, thus increase their return on investment (ROI). Online Vehicle Reservation: A tools through which customers can reserve available Vehicle online prior to their expected pick-up date or time. Customer’s registration: A registration portal to hold customer’s details, monitor their transaction and used same to offer better and improve services to them. bookings: Allows the customer to book space for a group in the case of weddings or corporate meetings. \\
	
	
	\newpage
	\hspace*{12pt} User
	
	• Register – This use case describes the activities of the customer to register online and become a member of the system. Customer's details are required as part of the registration. Login detail is automatically sent to the customer after successful registration.
	
	• Login – Once they have registered they need to login to avail the service at the needy time.
	
	• Make Reservation – This use case enable customer to search and make reservation. Notification is automatically send to the customer after the task is completed.
	
	• Return vehicle – This use case describes the event of customer returning the vehicle borrowed; the use case extends “process rental" use case from the Admin.
	
	
	Admin
	
	• Login–Registered Customers can login their accounts if they got their approval from the admin.
	
	• Add New vehicle– This use case is used by the staff to add new car to the company's fleet database. Staff will need to login to activate this use case.
	
	• Update Vehicle details - This use case is used by the staff to edit and modify Vehicle details whenever there is new renewal (insurance, road tax). It allows the company to keep up-to-date record of their fleet. 
	
	• View feedback– Using the feedbacks provided by the users/customers of the service hospitals have to maintain or improve their service.
	
	• Reply to customer’s feedback – This use case describes the event by which admin ends reply to customer's earlier feedback. It depends on `give feedback' use case from the customer. \\
	
	
	
	
	
	
	
	
	
	
	

\end{document}